A new tidy data structure to support exploration and modeling of temporal data

### 2019-08-21 tsibble.Rmd
updated code

```{r external, include = FALSE, cache = FALSE}
read_chunk('scripts/demo.R')
read_chunk('scripts/flights.R')
read_chunk('scripts/smart-meter.R')
```

@@

>>>>

```{r external, include = FALSE, cache = FALSE}
read_chunk('scripts/demo.R')
read_chunk('scripts/flights.R')
read_chunk('scripts/smart-meter.R')
ggplot2::theme_set(ggplot2::theme_bw())
```

@@

<!--
